Plotting the Single-Electron Solution to Schr\"{o}dinger's Equation with OpenCL

### 2010-05-05 paper/paper.tex
Add bibliography
Add some stuff to bibliography
Hardware specs, some manner of abstract

\usepackage[scaled=.92]{helvet}
\usepackage{times}
\usepackage{parskip}
\onlineid{0}

@@

Stuff

@@

Stuff

% \bibliographystyle{acmsiggraph}
% \nocite{*}
% \bibliography{proposal}

>>>>

\usepackage[scaled=.92]{helvet}
\usepackage{times}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{footmisc}
\onlineid{0}

@@

The realm of physics provides many readily parallelizable algorithms --- often involving the simple evaluation of a function at an enormous number of points in space --- which also happen to produce attractive visualizations. One such visualization is that of the probability distribution of the single electron within a hydrogen atom (or He$^+$, Li$^{2+}$, and so on). By evaluating Schr\"{o}dinger's equation at millions of points, one can construct a representation of the likely location of the electron --- the orbital cloud, if you will. Luckily, the evaluation of this function at a particular point is entirely independent of nearby points, so it is effectively perfect for parallelization. We will use OpenCL to develop and benchmark (on a varied array of hardware, from dated CPUs to very modern GPUs) an implementation of this algorithm which will produce a simple --- but attractive --- image of the atomic orbital of the single-electron hydrogen atom.

\section{Introduction}

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

asdfasdfadsf asdf adsf asdf asdf adfasdf adsf adf asfd

\section{Physics}

\section{Implementation}

@@

Benchmarks will be performed on a number of different OpenCL compute devices across a few different computers:

\begin{itemize}

\item ATI Radeon 4890, 800$\times$850MHz, 1GB VRAM, 250\$\footnote{All hardware prices listed are approximate launch prices.\label{fn:prices}}

\item Intel Core i7 620M, 2$\times$3333MHz, 4GB RAM, 332\$\footref{fn:prices}

\item Intel Core 2 Quad Q6600, 4$\times$3000MHz, 4GB RAM, 851\$\footref{fn:prices}

\item Intel Atom N270, 1$\times$1600MHz, 2GB RAM, 44\$\footref{fn:prices}

\end{itemize}

\section{Results}

\subsection{Large- vs. Small-scale Parallelism}

\subsection{Strong Scaling}

\subsection{Cost Effectiveness of Hardware}

\section{Future Work}

\section{Conclusion}

\bibliographystyle{acmsiggraph}
\nocite{*}
\bibliography{paper}
